### 2016-07-26 notions.tex
comments about privacy

\tsnote{Is this the right kind of indistinguishability anyway?  It seems to me that we want to say that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented.  One way to capture this would be indistinguishability with respect to the query set~$\calQ$: you are handed $(M,\aux)$ and you need to output a query~$q\in\calQ$ such that $q(S_0) \neq q(S_1)$.  But this doesn't really capture that $(M,\aux)$ on their \emph{own} do not leak information about the set.  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the Hamming weight of the array.)  I don't know, this is tricky... How do you handle the fact that, under our current syntax, $M$~may contain secrets, e.g. a PRP key?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

>>>>

\tsnote{Is this the right kind of indistinguishability anyway?  It seems to me that we want to say that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented.  One way to capture this would be indistinguishability with respect to the query set~$\calQ$: you are handed $(M,\aux)$ and you need to output a query~$q\in\calQ$ such that $q(S_0) \neq q(S_1)$.  But this doesn't really capture that $(M,\aux)$ on their \emph{own} do not leak information about the set.  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)  I don't know, this is tricky... How do you handle the fact that, under our current syntax, $M$~may contain secrets, e.g. a PRP key?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}
